---
title: "datalabvis03"
output: html_document
---
#Lab 02
##Author:Ajinkya Shinde

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(here) # to set file path if working from local file
library(tidyverse) # 

library(readr)
moma <- read_csv(here::here("data", "artworks-cleaned.csv"))
moma 

```


**1.How many paintings (rows) are in moma? How many variables (columns) are in moma?
Ans 
No. of paintings (rows) in moma are 2253
No. of variables (columns) in moma are  23**




```{r}
moma %>% 
  select(title,year_acquired,artist) %>%
  arrange(year_acquired)
```
**2.What is the first painting acquired by MoMA? Which year? Which artist? What title?
Ans 
The first painting with title "House by the railroad" acquired by moma in the year 1930 by the artist Edward Hopper**





```{r}
moma %>% 
  select(title,year_created,artist) %>%
  arrange(year_created)
```
**3.What is the oldest painting in the collection? Which year? Which artist? What title?
Ans 
The oldest painting with title "Landscape at Daybreak" is in the collection, created in the year 1930 by the artist Odilon Redon**




```{r}
distinct(moma %>% 
           select(artist))
```


**4.How many distinct artists are there?
Ans 979 distinct artists present in moma collection**


```{r}
count(moma,vars=artist,sort= TRUE) 
```
**5.Which artist has the most paintings in the collection? How many paintings are by this artist?
Pablo Piccaso has the most paintings with count of 55**



```{r}
count(moma,artist_gender)
```
**6.How many paintings by male vs female artists?
Ans Paintings made by female artists are  252
and paintings made by male artists are 1991**


```{r}

c_artist_g <-count(moma,artist_gender,artist)
count(c_artist_g,artist_gender)
```
**How many artists of each gender are there?
Ans Total female artists are 143 and male artists are 837**


```{r}
count(moma,year_acquired,sort=TRUE)
```
**In what year were the most paintings acquired?
Ans During 1985,the most paintings were acquired with count equal to 86**



```{r}
count(moma,year_created,sort=TRUE)

```

**In what year were the most paintings Created?
Ans  During 1977,the most paintings were created with count equal to 57**


```{r}
moma %>%
  filter(artist_gender == "Female" , n_female_artists == 1) %>% 
  select(year_acquired,year_created,artist,title) %>% 
  arrange(year_acquired)

```


**In what year was the first painting by a (solo) female artist acquired? When was that painting created? Which artist? What title?
Ans In the year 1937, the first solo female painting was acquired and created in the year 1912 by artist Natalia Goncharova with painting title "Landscape, 47"**

```{r}
ggplot(moma, aes(x=year_created, y=year_acquired)) + geom_point(alpha=0.05) + labs(x="Year Created", y ="Year Acquired" ) +ggtitle("MOMA keeps its Collection Current")+geom_abline(color="red")
```




**Plot year painted vs year acquired**

```{r}
f_moma <- moma %>% 
  filter(num_artists == 1)

ggplot(f_moma, aes(x=year_created, y=year_acquired)) + geom_point(alpha=0.05) + labs(x="Year Created", y ="Year Acquired" ) +ggtitle("MOMA keeps its Collection Current")+geom_abline(color="red") + facet_wrap(~artist_gender)

```

**Facet by artist gender**


  
```{r}
f_moma <- moma %>% 
  filter(height_cm<600,width_cm<760) %>% 
  mutate(cat_color = case_when (
    (height_cm/width_cm) < 1 ~ "Taller than wide",
    (height_cm/width_cm) > 1 ~ "Wider than tall",
    (height_cm/width_cm) == 1 ~ "Perfect square"
  ))

ggplot(f_moma, aes(x = width_cm, y = height_cm, colour = cat_color)) +
  geom_point(alpha = .5) +
  ggtitle("MoMA Paintings, Tall and Wide") +
  scale_colour_manual(name = "",
                      values = c("gray50", "#FF9900", "#B14CF0")) +      labs(x = "Width", y = "Height") 
```


**Plot painting dimensions**
```{r}
f_moma<-moma %>%
  filter(artist_gender == "Female" | artist_gender == "Male") %>% 
  mutate(area=height_cm * width_cm) %>%   
  select(year_created,artist_gender,area) %>% 
  group_by(year_created,artist_gender) %>% 
  summarize(tot_area=sum(area))

ggplot(f_moma, aes(x = year_created, y = tot_area, colour = artist_gender)) +
  geom_point(alpha = .5) +
  ggtitle("MoMA Paintings, Female artists vs Male artist painting area  distribution") +
 labs(x = "Year Created", y = "Total Area of painting in cm^2") +scale_y_log10()
```

**It seems that until 1910 , the total_area of paintings(including men and women) is under 10^5 magitude.However, then the total_area of paintings crossed the 10^5 border after 1910 and then crossed 1million boundary in 1940. Also, the total area of paintings crossed million for women approx around 1960-1975**



